--------------------------
title: "PA_1template.Rmd"
output: html_document
--------------------------

##This is the ProgramAssignment1's RMarkDown

- Firstly, you must downloaded the file activity.csv to the same Directory of your RMarkdown File. 

- Load the data. 
```{r loading, echo=TRUE}
  Activity<-read.csv("activity.csv")
```

- An Initial analisys of the  data structure
```{r InitAnalysis, echo=TRUE}
  str(Activity)
  names(Activity)
  head(Activity)
```

- Getting only the valid Lines (ignoring the missing values)
```{r IgnoreMissing, echo=TRUE}
 ValidActivity<-Activity[!is.na(Activity$steps),]
```
- Grouping the total steps per day
```{r totalstepsperday, echo=TRUE}   
   totalstepsperday<-tapply(ValidActivity$steps,ValidActivity$date,sum)   
```

- Looking at the data structure
```{r echo=TRUE}
  str(totalstepsperday)
  names(totalstepsperday)
  head(totalstepsperday)
```

- I don't know why, but there are some results equals to NA. Anyway, I can ignore it and obtain the total of steps per day without NAs
```{r echo=TRUE}
   totalstepsperday<-totalstepsperday[!is.na(totalstepsperday)]
   totalstepsperday
```

- Plotting a histogram of the data
```{r histogram, echo=TRUE}
hist(totalstepsperday, breaks=ceiling(1+3.32*log(dim(totalstepsperday))), col="blue",labels=TRUE,main="Frequency of number of steps per day")
```

- Obtaining the mean of steps per day
```{r meanstepsperday, echo=TRUE}
 meanofstepsperday<-mean(totalstepsperday)
 meanofstepsperday
```

- Obtaining the median value of the values observed for steps per day
```{r medianstepsperday, echo=TRUE}
  medianofstepsperday<-median(totalstepsperday)
  medianofstepsperday
```

- Grouping the average number of steps per interval
```{r totalperinterval, echo=TRUE}
  stepsperinterval<-tapply(ValidActivity$steps,ValidActivity$interval,mean)
```

- Looking at the data structure
```{r echo=TRUE}
  str(stepsperinterval)
  head(stepsperinterval)
```

- Plotting a single graphic of Number of steps by Intervals
```{r plotstepsperinterval,echo=TRUE}
   plot(row.names(stepsperinterval), stepsperinterval,xlab="Label of the Intervals (5 minutes each)", ylab="Number of steps",main="Mean number of steps by intervals", type="l")
```

- Obtaining the interval with maximum mean value of number of steps
```{r maxintervalmean, echo=TRUE}
   x<-0
   largest<-0
   for (i in 1:dim(stepsperinterval)){
     if (stepsperinterval[i]>largest){
       largest<-stepsperinterval[i]
       x <- i
     }
   }
   print("Order of the Interval:")
   print(i)
   print("Label of the Interval:")
   names(stepsperinterval[x])
```

